Hire Ed: Job Market Dynamics for Tenure-Track Faculty Positions in Archaeology

### 2024-12-20 analysis/paper/article.qmd
resolve merge conflict
clean up copy-paste, test html comment in visual model

gitcreds::gitcreds_set()
library(usethis)
use_git_config(user.name = "Jess Beck")
---
title: "Hire Ed: Job Market Dynamics for Tenure-Track Faculty Positions in Archaeology"
author:
  - Ben Marwick:
      correspondence: "yes"
      email: bmarwick@uw.edu
      orcid: 0000-0001-7879-4531
      institute:
        - uw
  - Anne Marie Poole:
      institute: uw
      orcid: xxx
  - Ailin Zhang:
      institute: uw
      orcid: xxx
  - Setareh Shafizadeh:
      orcid: 0000-0003-2231-4310
      institute: uw
  - Jess Beck:
      orcid: 0000-0002-7387-2307
      institute:
        - ucd
institute:
  - uw: Department of Anthropology, University of Washington, Seattle, USA
  - ucd: School of Archaeology, University College Dublin, Ireland

@@

The aim of this paper is to TEACH JESS HOW TO USE QUARTO AND GITHUB, UNFORTUNATELY FOR JESS. <!-- It would be nice if you could make comments in the visual mode and not just in source mode, unfortunate --> We had two aims: to determine if disciplinary trends can be discerned in the topical, geographic, and method foci of the positions advertised; and to investigate how the requirements for applicants have changed over time.

>>>>

---
title: "Hire Ed: Job Market Dynamics for Tenure-Track Faculty Positions in Archaeology"
author:
  - Ben Marwick:
      correspondence: "yes"
      email: bmarwick@uw.edu
      orcid: 0000-0001-7879-4531
      institute:
        - uw
  - Anne Marie Poole:
      institute: uw
      orcid: xxx
  - Ailin Zhang:
      institute: uw
      orcid: xxx
  - Setareh Shafizadeh:
      orcid: 0000-0003-2231-4310
      institute: uw
  - Jess Beck:
      orcid: 0000-0002-7387-2307
      institute:
        - ucd
institute:
  - uw: Department of Anthropology, University of Washington, Seattle, USA
  - ucd: School of Archaeology, University College Dublin, Ireland

@@

The aim of this paper is to TEACH JESS HOW TO USE QUARTO AND GITHUB, UNFORTUNATELY FOR JESS. <!-- It would be nice if you could make comments in the visual mode and not just in source mode, unfortunate --> We had two aims: to determine if disciplinary trends can be discerned in the topical, geographic, and method foci of the positions advertised; and to investigate how the requirements for applicants have changed over time. <!-- yes we can make and view comments in visual mode, my mistake to think it was not possible -->
